EpisoPass: Password Management based on \\ Episodic Memories

### 2016-04-13 paper/UIST2016/paper.tex
...

\title{EpisoPass: Password Management based on Episodic Memories}

@@

We propose a new password manager \textit{EpisoPass} that supports
generating strong passwords based on users' secret episodic memories.
When a user want to enter a password,
EpisoPass shows the user multiple secret questions and possible answers to
each question, and
EpisoPass generates a password by substituting characters of the
'seed' string based on the user's selections.
If the right answers to the questions are known only to the user,
the password cannot be guessable by other people, and
various strong passwords can be easily managed
without having master passwords or secret devices that are
usually required for password managers.

% We introduce a password generation/management system called EpisoPass,
% which converts a seed string into a password using the user's
% episodic memories represented as a set of questions and answers
% which can be solved only by the user.
% Using EpisoPass with well-defined questions and answers,
% a user can always retrieve various passwords without worrying about
% remembering secret information.

@@

Passwords have been used for various Web services and applications
for a long time, and currently the most popular authentication method on the Internet
without doubt.
Since short passwords are easy to crack and
using the same password for different services is unsafe,
different long passwords should be used for different services,
but remembering many long passwords is almost impossible for ordinary people.
%
According to Flor\^{e}ncio's reearch in 2007,
people use 6.5 passwords on 25 Web services on average, and
4.28\% of the users forget their passwords in 3 months\cite{Florencio:2007:LSW:1242572.1242661}.

@@

People are frequently asked to register a password when
they try to use a new service.

@@

In spite of these attempts,
password-based authentication is still the most
convenient and strong method\cite{Bonneau},
and it is not supposed to become extinct
in a short period of time\cite{Herley:2009:PSS:1601990.1602010}.

@@

If we have to live with password-based authentication systems,
we have to devise a way to handle many passwords somehow.
For handling many strong passwords,
various password managers (PMs) have been proposed
{\PW}管理システムは
ひとつの「マスター{\PW}」を利用して他のすべての{\PW}を管理するもので、
暗号化されたデータベースに{\PW}を格納するもの%
\cite{OnePassword}%
\cite{Dashlane}%
\cite{ミルパス}%
\cite{LastPass}%
\cite{KeyPass}%
\cite{NortonIDSafe}%
\cite{IDManager}%
が多いが、サービス名をもとにマスター{\PW}を変換することによって
複数の{\PW}を生成するシステム\cite{SuperGenPass}もある。
両者ともにマスター{\PW}の記憶は必須であり、
マスター{\PW}を盗まれたり忘れたりする危険がある。

Password managers remember users' passwords and help them use passwords for different services.
Althought PMs are useful, users should remember a 'master password' for
keeping the secret data, and
some password managers are not available on all environment.

@@

We believe that the biggest problem of brain-based authentication systems is that
users cannot keep new memories which corresponds to authentication methods,
and we believe that
it is far better to ``generate'' symbols for authentication based on
users' episodic memories which they can never forget.

We believe that a password manager should have the following features.
(1) It should be available on any platform including PCs, smartphones, and the Web.
(2) Users should not have secret information (e.g. master password) or special device.
(3) Rely only on the information in the user's brain.

We propose a password manager called \textit{EpisoPass}, that generates strong passwords
based on the user's secret episodic memories that the user can never forget,
instead of systems based on remembering semantic memories.

@@

EpisoPass is a password manager that supports generating
strong passwords based on users' secret episodic memories.
A user provides a seed string and many question-answer pairs to EpisoPass,
and a password is generated based on the user's selections.

\begin{enumerate}
\item Provide a long string for generating a password.
We call it the ``seed string''

\item Create many question strings based on personal
secret episodic memories that the user never forgets,
and provide many candidate answers only one of which is the correct one.

% 忘れることがない個人的な{\EM}にもとづく{\SQ}を複数作成し、
% それぞれについてひとつの正答と複数の偽答を用意する。

\item Based on the user's selection of answers,
substitute characters in the seed string and generate a
string for password.

% 質問と回答の組にもとづいて{\SS}に換字操作を行なう。
% すべてに正しく回答したとき生成される文字列を{\PW}として利用する。

\end{enumerate}

@@

@@

Figure \ref{web1} shows how to generate a password
on EpisoPass running on a browser.
Many questions related to episodic memories are shown to the user
as well as many candidate answers are shown for each question.
When a user clicks and selects one of the answers for each question,
the seed string is converted to a random-looking string
based on the selections.
If the q-a is based on the user's episodic memories and
nobody knows the correct answer,
only the user can select the set of right answers and
use the converted string as the password.

@@

Here, ``\textsf{Twitter123456}'' is provided as the seed string,
and according to the selection to four questions,
the seed string is converted to strings like
``\textsf{Mfveabn574923}'', which can be used as the password for Twitter.

@@

In this way, different selections yields different password strings, and
the password string generated after selecting all correct answers can be
used as the password for the service. (Twitter in this case.)

@@

The first secret question in Figure \ref{web1}
is based on the author's episodic memory at elementary scholl,
and the last secret questionois related to a recent event which the author
thinks he can never forget.
All the questions are related to the author's episodic memory
that he never forgets, and nobody else knows which one of the
candidate answers is the right answer.

% 最初の{\SQ}は筆者の小学校の同級生に関するもので、
% 最後の質問は数年前の体験に関するものである。
% これらの質問は古い{\EM}にもとづいており、
% 筆者が将来答を忘れることはほとんど考えられないが、
% 本人以外がこのような質問に答えることは難しいので
% 正しい{\PW}を得ることはできない。

Questions and answers can be edited on a browser, and they can be
saved on the server by clicking the ``save on server'' button.
Although questions and answers are saved on the server,
no information about the correct answer is saved anywhere,
so nobody can tell which one is the correct answer.

@@

When we change the secret string to ``\textsf{Facebook123456}'',
the generated password changes to Figure \ref{web2}.
In this way, we can generate different passwords for
different services just by changing the seed string.

@@

% {\SS}を「\textsf{Facebook123456}」に変更すると、生成される{\PW}は図\ref{web2}のように変化する。
% このように、サービスごとに異なる{\SS}を利用することによって
% 様々な{\PW}を簡単に生成できる。

@@

\subsubsection{Android application}

@@

If a user doesn't like to use EpisoPass service on the net,
he can use an EpisoPass application on Android
which does not use any network connection.
After registering questions and answers on the EpisoPass service,
the user can download an Android application from the server
which contain all the information required for generating passwords.
(The application is compiled and built on the server.)

@@

@@

\subsection{Algorithm for calculating password from selections}

\section{Discussions}

\subsection{Advantages of using EpisoPass}

\paragraph{Unforgettable}

%   絶対忘れない
%     30年忘れなかったものは40年忘れないだろう

The biggest advantage of using EpisoPass is that
users don't have to worry about forgetting or losing passwords.
Users of EpisoPass can always save the seed string and question-answer
pairs at any place, and easily generate passwords by answering questions.
If the question is based on old episodic memories,
there is little chance of forgetting correct answers and losing passwords
generated from the selections.
If the episodic memory is based on 20 years ago and the user clearly
remembers it at this moment, it is unlikely that he forgets the episode after
several years.

\paragraph{Usable for everyone}

%   老人など、頭が弱くても対応できる

Not everyone is familiar with handling passwords.
Even experienced computer users sometimes use weak passwords,
since choosing a good password is not a straightforward task.
Using EpisoPass, people who cannot create and remember strong passwords
can easily generate strong passwords just by providing secret
questions and answers.
With a good interface, people can even use various password-based
services without noticing the problem of passwords.

\paragraph{Easy to change passwords}

On some systems, users are requested to change passwords periodically
to strenghen security.
A user can generate a new strong password by using a randam character generator
on a password manager, but he might want to old passwords in case some trouble happens.
Using EpisoPass, user can just provide a date-related question-answer pairs,
and generate different strong passwords based on the answer.
(Figure xxx)

\paragraph{All information can be put public}
%   全情報を公開して大丈夫
%     マスターパスワードが要らない
%     秘密裏などは誤って流出する可能性があるが...

\paragraph{Strong passwords can be generated}
%   強度を自由に設定できる

\paragraph{Image-based authentication}
%   画像を使える

\paragraph{Simple implementation}
%   実装が簡単

\paragraph{パスワード自体の漏洩の心配が不要}
% 聞かれてもわからないし書き留める必要がないからウッカリもらす可能性はない
% ローカルに実行すればネットでもれる心配もない

\subsection{Risks of using EpisoPass}

\paragraph{Security strength of EpisoPass}
% ■ 安全性

% {\PW}は長年利用されているため
% 強度や実際の運用に関して多くの研究が存在するが%
% \cite{Hayashi:2011:DSP:1978942.1979326}%
% \cite{Komanduri:2011:PPM:1978942.1979321}% どういうパスワードが強いか
% 、{\SQ}の強度に関しては充分研究されていない。
% {\EP}の運用実績は長くないが安全性などについて考察を行なう。

There have been many studies on the strength of passwords
\cite{Hayashi:2011:DSP:1978942.1979326}%
\cite{Komanduri:2011:PPM:1978942.1979321},% どういうパスワードが強いか
but the strength of secret questions are not studied a lot so far.

% {\EP}で選択枝が10個の{\SQ}を8個使用する場合、
% 総当たりで{\PW}を生成するには
% 1億($10^8$)通りの試行が必要であり、
% % エントロピーは26.6 ($ = 8 \times \log_2 10$) ビット
% エントロピーは26.6ビットとなる。

When we use 8 secret questions with 10 answers,
100 million ($10^8$) trials should be performed to check
all the combinations of the answers,
and the entropy of the system is 26.6 ($ = 8 \times \log_2 10$) bits.

英字からランダムに8文字を並べて作成した{\PW}のエントロピーは37.6ビットになるが、
``\textsf{pmvixuzq}''のように全く意味のない{\PW}を記憶して利用することは少ないため、
実際に利用される{\PW}のエントロピーは20ビット程度と考えられているので\cite{NIST}、
{\SQ}と選択枝の数を10個程度用意すれば
通常の{\PW}と同程度の強度が期待できることになる。
%
総当たり攻撃が可能なオフライン運用ではエントロピーの大きさは重要であるが、
オンラインサービスでは
{\PW}入力を何度か間違えるとサービスがブロックされるのが普通なので、
それほど長い{\PW}を用意する必要は無いと考えられている\cite{Florencio:2007:SWP:1361419.1361429}。

\subsection{Selecting secret questions}

@@

Selecting good questions is very important for using EpisoPass.
The episode related to the question should not be known to other people,
and the episode should be an unforgettable one.
%

@@

Specifically, questions like the following are good candidates for
questions used in EpisoPass.

@@

@@

{\scriptsize
\bibliographystyle{acm-sigchi}
\bibliography{paper}
}

@@

* 秘密の質問に入れる偽装の答えをどこにメモしたか忘れるという事もしばしば

=> 問題も答も公開しておけば忘れることはないでしょう。

@@

* EpisoPassのフィッシングサイトができたらどうしましょう

=> 完全にローカルHTMLかローカルアプリで使えば安心でしょう。

>>>>

\title{EpisoPass: Password Management based on \\ Episodic Memories}

@@

%
% We introduce a password generation/management system called EpisoPass,
% which converts a seed string into a password using the user's
% episodic memories represented as a set of questions and answers
% which can be solved only by the user.
%
% Using EpisoPass with well-defined questions and answers,
% a user can always retrieve various passwords without worrying about
% remembering secret information.

We propose a password manager \textit{EpisoPass} that supports
generating strong passwords based on the user's secret and unforgettable
episodic memories.
%
To use EpisoPass,
a user first collects question-answer pairs related to his episodic memory
and registers them with many fake answers.
%
When a user wants to generate a password,
EpisoPass shows the questions and lists of possible answers and asks
the user to select correct ones.
Then EpisoPass generates a password by substituting characters of the
seed string based on the answer selections.
%
If only the user knows the correct answer,
% If the right answers to the questions are known only to the user,
the password cannot be guessable by other people, and
various strong passwords can be easily managed
without using master passwords or secret devices that are
usually required on conventional password managers.
%

@@

Passwords have been used for various Web services and applications
for a long time, and currently the most popular authentication method on the Internet.
%
Since short passwords are easily guessed by atackers, and
using the same password for different services is unsafe,
different long passwords should be used for different services.
However,
remembering many long passwords is almost impossible for ordinary people.
%
% According to Flor\^{e}ncio,
According to a research in 2007,
people use 6.5 passwords on 25 Web services on average, and
4.28\% of the users forget their passwords in 3 months\cite{Florencio:2007:LSW:1242572.1242661}.

@@

% People are frequently asked to register a password when
% they try to use a new service.

@@

In spite of such attempts,
password-based authentication is still the most
convenient and strong method\cite{Bonneau},
and it is not supposed to get extinct
in a short period of time\cite{Herley:2009:PSS:1601990.1602010}.

@@

If we have to live with password-based authentication systems,
we have to devise some ways to handle many passwords, and
various ``password managers'' have been proposed
for handling many strong passwords.
%
{\PW}管理システムは
ひとつの「マスター{\PW}」を利用して他のすべての{\PW}を管理するもので、
暗号化されたデータベースに{\PW}を格納するもの%
\cite{OnePassword}%
\cite{Dashlane}%
\cite{ミルパス}%
\cite{LastPass}%
\cite{KeyPass}%
\cite{NortonIDSafe}%
\cite{IDManager}%
が多いが、サービス名をもとにマスター{\PW}を変換することによって
複数の{\PW}を生成するシステム\cite{SuperGenPass}もある。
両者ともにマスター{\PW}の記憶は必須であり、
マスター{\PW}を盗まれたり忘れたりする危険がある。

Password managers remember users' passwords and help them enter
passwords on various services.
Althought password managers are useful,
users are usually forced to remember a ``master password''
or a special hardware device
for safely handle password managers, and
password managers usually run on limited devices.

@@

If we don't want to carry any special device for authentication,
all the information required for the authentication should be
kept in the brain.
%
However, we believe that the biggest problem of brain-based authentication is that
users cannot keep memories like long passwords or master password.
For this reason, we believe that
it is far better to ``generate'' something for the authentication,
based on users' episodic memories which they can never forget.

% We believe that a password manager should have the following features.
% (1) It should be available on any platform including PCs, smartphones, and the Web.
% (2) Users should not have secret information (e.g. master password) or special device.
% (3) Rely only on the information in the user's brain.

We propose a password manager \textit{EpisoPass}, that generates strong passwords
based only on the user's secret episodic memories that the user can never forget.

@@

EpisoPass is a password manager that supports generating
strong passwords based on users' secret episodic memories.
%
% Before using EpisoPass for generating passwords,
% a user provides a seed string and many question-answer pairs to EpisoPass,
% and a password is generated based on the user's selections.
%

According to Wikipedia, ...

@@

Password generation on EpisoPass is performed through the following procedures:

\begin{enumerate}
\item A user registers many question texts based on the user's personal
secret episodic memories that the user never forgets,
and provide a correct answer and many fake answers.

\item The user provides a long ``seed string'' for each service that requires
a password.

\item EpisoPass shows the registered data to the user so that
the user can select an answer for each question.
Based on the user's selection,
EpisoPass substitute characters in the seed string and generate different
strings for different selections.
The user copies the string calculated when correct answers are selected,
and use it as the password for the service.
\end{enumerate}

@@

Figure \ref{web1} shows how to generate a password
on EpisoPass running on a browser.
Many questions related to the user's episodic memories are shown to the user,
and many candidate answers are also shown for each question.
When a user clicks and selects one of the answers for each question,
the seed string is converted to a random-looking string
based on the selections.
When the user selects the right answer to all the questions,
the right password is calculated and shown at the top.

% If the q-a is based on the user's episodic memories and
% nobody knows the correct answer,
% only the user can select the set of right answers and
% use the converted string as the password.

@@

In Figure \ref{web1},
``\textsf{Twitter123456}'' is provided as the seed string,
and according to the selections to the four questions,
the seed string is converted to a string like
``\textsf{Mfveabn574923}'',
which can be used as the password for Twitter.

@@

In this way, different selections yields different password strings and
the password string generated after selecting correct answers can be
used as the password for the service. (Twitter in this case.)

@@

The first secret question in Figure \ref{web1}
is based on the author's episodic memory at elementary scholl,
and the last secret question is related to a more recent event
which the author thinks he can never forget.
All the questions are related to the author's episodic memories
that he thinks he never forgets, and nobody else knows which one of the
candidate answers is the right one.

Questions and answers can be edited directly on a browser, and they can be
saved on the server by clicking the ``save on server'' button.
The Q-A data sets are saved on the server,
but no information about the correct answer or the
generated password is saved on the server.

@@

When we change the secret string to ``\textsf{Facebook123456}'',
the generated password changes to ``\textsf{Xxxxxxx123456}'',
as shown in Figure \ref{web2}.
In this way, we can generate different passwords for
different services just by changing the seed string.

@@

%アルゴリズムはここ? Algorithm

Character substitution is performed based on the hash value
calculated from putting all the selected answers.
For example, if the user selects ``answer1-3'' to the question ``question1'',
a hash value calculated from  ``\texttt{question1:answer1-3}''
is used for the substitution.
Details of the algorithm is showin in Appedix.

@@

\subsection{Android application}

@@

If a user doesn't like to use EpisoPass service on the browser,
he can use an EpisoPass application on Android
which does not use any network connection.
After registering questions and answers on the EpisoPass service,
the user can download an Android application from the server
which contain all the information required for generating passwords.
(The application is compiled and built on the server.)

@@

(Figure of Android app)

@@

\section{DISCUSSIONS}

In this section, we discuss the advantages and caveats of
using EpisoPass.

\subsection{Unforgettability}

The biggest advantage of using EpisoPass is that
users don't have to remember passwords of any kind and
they can stop worrying about password-related troubles.
%
Users of EpisoPass can save the seed string and question-answer
pairs at any place, and easily generate passwords by answering questions.
If the question is based on old unforgettable episodic memories,
there is little chance of losing passwords.
If the user's memory is related to an episode of 20 years ago and the user clearly
remembers it now, it is unlikely that he forgets the episode after 10 years.

\subsection{Selecting good questions}

@@

The quality of secret questions is the key to using EpisoPass.
The episode related to the question should not be known to other people,
and the episode should be unforgettable.
%
Finding such episodes seems difficult at first, but
when we try to remember experiences of old days,
we can recall many trivial episodes which are not
important for other people.
%
Questions like the following are good candidates for
questions used in EpisoPass.

@@

@@

\subsection{Usable for everyone}

Not everyone is familiar with handling passwords.
Even experienced computer users have trouble with passwords,
since choosing a good password is difficult and people forget passwords frequently.
Using EpisoPass, people who cannot create and remember strong passwords
can easily generate strong passwords just by providing secret
questions and answers.
By integrating EpisoPass into existing password-based services,
people can even use such services without noticing the problem of passwords.

\subsection{Easy to change passwords}

On many services, users are requested to change passwords periodically
to strenghen security.
A user can generate a new strong password by using a randam character generator
on a password manager, but he might want to old passwords in case some trouble happens.
Using EpisoPass, user can just provide a date-related question-answer pairs,
and generate different strong passwords based on the answer.

(Figure xxx)

\subsection{Security strength of EpisoPass}

There have been many studies on the strength of passwords
\cite{Hayashi:2011:DSP:1978942.1979326}%
\cite{Komanduri:2011:PPM:1978942.1979321},% どういうパスワードが強いか
but the strength of secret questions has not been studied.
%
% {\EP}で選択枝が10個の{\SQ}を8個使用する場合、
% 総当たりで{\PW}を生成するには
% 1億($10^8$)通りの試行が必要であり、
% % エントロピーは26.6 ($ = 8 \times \log_2 10$) ビット
% エントロピーは26.6ビットとなる。
%
When we use 10 secret questions with 20 answers,
1 billion ($20^8$) trials should be performed to check
all the combinations of the answers,
and the entropy of the system is 43.2 ($ = 10 \times \log_2 20$) bits.  % 10.0 * (Math.log(20.0)/Math.log(2.0))
%
% 英字からランダムに8文字を並べて作成した{\PW}のエントロピーは37.6ビットになるが、
% ``\textsf{pmvixuzq}''のように全く意味のない{\PW}を記憶して利用することは少ないため、
% 実際に利用される{\PW}のエントロピーは20ビット程度と考えられているので\cite{NIST}、
% {\SQ}と選択枝の数を10個程度用意すれば
% 通常の{\PW}と同程度の強度が期待できることになる。
%
It is almost the same entropy as using random 8-character English letters
as a password, in which case the entropy is 45.6 bits, 
and this level of strength is considered to be enough for most Web services,
where online blute-force attack is impossible\cite{Florencio:2007:SWP:1361419.1361429}.

% 総当たり攻撃が可能なオフライン運用ではエントロピーの大きさは重要であるが、
% オンラインサービスでは
% {\PW}入力を何度か間違えるとサービスがブロックされるのが普通なので、
% それほど長い{\PW}を用意する必要は無いと考えられている\cite{Florencio:2007:SWP:1361419.1361429}。

\subsection{Issues on EpisoPass questions}

\subsection{All information can be put public}

Questions and answers can be put on a public place
if enough amount of questions and fake answers are provided.
%
Keeping the secret of something is always a pain for many people including
the authors, but if the whole questions and answers used on EpisoPass
can be put on a public place,
handling it becomes very easy.
Usually we have to be very careful about handling
secret information like passwords, secret key for SSH, etc.
so that they are not copied or saved to unsafe places.
On the other hand,
we can save the EpisoPass data as a plain text file and put it at
any place without great care, since malicious person cannot calculate
passwords without having the owner's episodic memories.

%   全情報を公開して大丈夫
%     マスターパスワードが要らない

\subsection{Risk of password leak}

% 聞かれてもわからないし書き留める必要がないからウッカリもらす可能性はない
% ローカルに実行すればネットでもれる心配もない

% \subsection{Strong passwords can be generated}
%   強度を自由に設定できる

\subsection{Using images}
%   画像を使える

\subsection{Simple implementation}
%   実装が簡単

@@

{% \scriptsize
\bibliographystyle{acm-sigchi}
\bibliography{paper}
}

@@

@@
